Exploring the Validity Range of PLL Analytical Models

### 2025-06-02 CaseStudies/Example3_2_LimitsoftheTheorySoFar/Report/article/article.qmd
Finishing report 3.2.

plt.axvline(t_step * 1e6, color='purple', linestyle='--', linewidth=1.0, label='Step Frequency Instant')

@@

# Plotagem
plt.figure(figsize=(8, 6))
plt.plot(t_out * 1e6, phi_in, linestyle=':', color='black', linewidth=0.8, label='Reference Phase')
plt.plot(t_out * 1e6, phi_out, label='Feedback Phase')
plt.plot(t_out * 1e6, tracking_error, label='Phase Error')
plt.xlabel('Time (µs)')
plt.ylabel('Phase (rad)')
plt.grid(True)
plt.legend()
plt.tight_layout()
plt.show()

@@

# Linhas horizontais em ±1% do valor de pico (em torno de zero)
plt.axhline(tol, color='purple', linestyle='--', linewidth=1.0)

@@

# Plotagem
plt.figure(figsize=(8, 6))
plt.plot(t * omega_n_meas, vc_response, label='Voltage Control')
plt.axhline(final_value, color='red', linestyle='--', linewidth=0.8, label='Reference Voltage')

@@

# Behavioral Simulation

>>>>

plt.axvline(t_step * 1e6, color='purple', linestyle='--', linewidth=1.2, label='Step Frequency Instant')

@@

# Plotagem
plt.figure(figsize=(8, 6))
plt.plot(t_out * 1e6, phi_in, linestyle=':', color='black', label='Reference Phase')
plt.plot(t_out * 1e6, phi_out, label='Feedback Phase')
plt.plot(t_out * 1e6, tracking_error, label='Phase Error')
plt.xlabel('Time (µs)')
plt.ylabel('Phase (rad)')
plt.grid(True)
plt.legend()
plt.tight_layout()
plt.show()

@@

# Linhas horizontais em ±1% do valor de pico (em torno de zero)
plt.axhline(tol, color='black', linestyle=':')

@@

# Plotagem
plt.figure(figsize=(8, 6))
plt.plot(t * omega_n_meas, vc_response, label='Voltage Control')
plt.axhline(final_value, color='black', linestyle=':', label='Reference Voltage')

@@
